Fully Generalized Compilation

### 2017-02-06 papers/paper.tex
Improves paper outline

% Packages for showing source code
\usepackage{listings}
\usepackage{color}

@@

\lstset{frame=tb,
language=C,
aboveskip=1mm,
belowskip=1mm,
showstringspaces=false,
columns=flexible,
basicstyle={\small\ttfamily},
numbers=none,
numberstyle=\tiny\color{gray},
keywordstyle=\color{blue},
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
breaklines=true,
breakatwhitespace=true,
tabsize=3
}

% Package for flowcharts/diagrams

@@

% ==================================================
% Begin Paper
% ==================================================

@@

\section{Abstract}

Assuming that two languages are \textit{isomorphic}, one syntax can be converted to another if given an adequate description of each syntax's grammar.
At an abstract level, this conversion is entirely practical. 
Progtran is an investigation into the feasibility of a \textbf{Fully Generalized Compiler}, a multi-language source-to-source compiler. 
Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?

\section{Introduction}

@@

\section{Methods}

\subsection{Grammars}
\subsection{Constructors}
\subsection{AST Transformations}

@@

\section{Results}
\subsection{Quicksort Cython Comparison}

@@

Output for 1000 sorting iterations:
\begin{center}
    \begin{verbatim}
        Transpile speedup:
        13.335545461765733
        Cython speedup:
        13.9866371311344
        Transpile : Cython comparison (1> indicates transpile is faster than cython)
        0.9534490197132998
    \end{verbatim}
\end{center}

@@

>>>>

% ================================================================================= 
% Package for showing source code
% =================================================================================

\usepackage{listings}
\usepackage{color}

@@

\lstset{frame=tb,
language=C,
aboveskip=.5mm,
belowskip=.5mm,
showstringspaces=false,
columns=flexible,
basicstyle={\scriptsize\ttfamily},
numbers=none,
numberstyle=\tiny\color{gray},
keywordstyle=\color{blue},
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
breaklines=false,
breakatwhitespace=true,
tabsize=3
}

% ================================================================================= 
% Package for flowcharts/diagrams
% =================================================================================

@@

% ==================================================
% Paper
% ==================================================

@@

% ==================================================
\section{Abstract}
% ==================================================

Assuming that two languages are \textit{isomorphic}, one language can be converted to another if given an adequate description of each language's grammar.
At an abstract level, this conversion is entirely practical. However, in practice,  
Progtran is an investigation into the feasibility of a \textbf{Fully Generalized Compiler}, a multi-language source-to-source compiler. 
Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?

% ==================================================
\section{Introduction}
% ==================================================

@@

% ==================================================
\section{Methods}
% ==================================================

\subsection{Traditional Compilation}
Brief description of how compilers work

\subsection{Abstracting Language Definitions}
Description of grammar, transformation, and constructor files

\subsection{Grammars}
Influence of formal grammars

Description of grammar file implementations

\subsection{AST Transformations}

Reasoning for and description of AST-transformations

\subsection{Constructors}

Description of Constructor implementation

\subsection{Compilation in Glossa}
Given all of the above details, how does compilation in Glossa compare to the traditional compilation process?

(Grammar/Transform/Construction rules are read at run-time)

@@

% ==================================================
\section{Applications}
% ==================================================

\subsection{Re-implementation of Cython and 2to3}
Description of implementing these two pieces of software with glossa

\subsection{Cython}
\subsection{2to3}

\subsection{Comparisons and Benchmarks}

\subsection{Simple code porting}
Reference work on 2to3, talk about FORTRAN and similar conversions

\subsection{Language Creation}
Description of implementing new programming languages using glossa

\subsection{Language Design and Modification}
\subsection{Glossa as a pre-processor}

% ==================================================
\section{Results}
% ==================================================

\subsection{Results Overview}

2to3 comparison

Cython comparison

GHC comparison

\subsection{Quicksort Cython Comparison}

@@

Output for 1000 sorting iterations:
\begin{center}
    \begin{verbatim}
        Transpile speedup:
        13.335545461765733
        Cython speedup:
        13.9866371311344
        Transpile : Cython comparison 
        0.9534
    \end{verbatim}
\end{center}

@@

% ==================================================
\section{Conclusion}
% ==================================================
